---
title: "Researcher Mentoring Program for Early-Career Researchers (2025)"
subtitle: "Mentor and Mentee Pairing"
#author: "Jen Beaudry"
date: "January 2025"
output: pdf_document
editor_options: 
  chunk_output_type: console
header-includes:
  - \usepackage{titling}
    \setlength{\droptitle}{-2cm} # removes some of the white space above title
  - \pretitle{\begin{center}
    \includegraphics[width=1.5in, height=1.5in]{flinders-university-horizontal-master.png}\LARGE\\} # adds logo
  - \posttitle{\end{center}}
  - \usepackage{fancyhdr}
  - \fancypagestyle{plain}{\pagestyle{fancy}} # sets the footer on page 1
  - \pagestyle{fancy} # sets the footer on page 2 and beyond
  - \fancyhf{} # clears existing header & footer
  - \renewcommand{\headrulewidth}{0pt} # removes the line from the header
  - \fancyfoot[L]{Jen Beaudry} # my name in footer
  - \fancyfoot[R]{\thepage} # page number in foooter
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, 
                      include = FALSE, 
                      fig.path = here::here("figs"))

options(knitr.duplicate.label = "allow") # use this when you use the child files
```

```{r notes to self, include=FALSE}

# we have four back up mentors: 
 # mentor_42; mentor_28; mentor_38; mentor_22

```

```{r functions, include=FALSE}

styler_pdf <- function(dat) {
  dat %>%
     kable_styling(full_width = F, 
                latex_options = c("striped", "HOLD_position"))
}

```


```{r library, include=FALSE}

library(here)
library(tidyverse)
library(kableExtra)
library(janitor)

source(here("..", "functions", "read_qualtrics.R"))

```


```{r load data, include=FALSE}

# mentor data

df_tor <- read_csv(here::here("00_data", "processed_data", "eoi_mentor_eligible.csv"), lazy = FALSE)

# mentee data

df_tee <- read_csv(here::here("00_data", "processed_data", "eoi_mentee_eligible.csv"), lazy = FALSE)

# load metadata for the area variables

meta_tor <- read_csv(here::here("00_data", "raw_data", "metadata_eoi_mentor.csv"), lazy = FALSE) %>%
    filter(scale == "areas")

# load metadata for the area variables

meta_tee <- read_csv(here::here("00_data", "raw_data", "metadata_eoi_mentee.csv"), lazy = FALSE) %>%
    filter(scale == "areas")

```


```{r code factors, include=FALSE}

df_tor$college <- as.factor(df_tor$college)
df_tee$college <- as.factor(df_tee$college)

df_tor$id <- as.factor(df_tor$id)
df_tee$id <- as.factor(df_tee$id)

#df$`name and college` <- as.factor(df$`name and college`)

```


```{r add pairing information for mentors}

# this is based on the pairing process that I  completed. I am running this
  # up here so I can rerun some of the tables to show me only the folks who 
  # still need to be paired. I will not run this later for the final report.
  # The second number is the pair number.

# removing the one mentee who withdrew (mentee_30) and one mentor who withdrew (mentor_13)

df_tor <- df_tor %>% 
  mutate(pair = case_when(id %in% "mentor_25" ~ "01",
                          id %in% "mentor_15" ~ "02",
                          id %in% "mentor_44" ~ "03",
                          id %in% "mentor_29" ~ "04",
                          id %in% "mentor_10" ~ "05",
                          id %in% "mentor_27" ~ "06",
                          id %in% "mentor_35" ~ "07",
                          id %in% "mentor_47" ~ "08",
                          id %in% "mentor_8" ~ "09",
                          id %in% "mentor_39" ~ "10",
                          id %in% "mentor_23" ~ "11",
                          id %in% "mentor_20" ~ "12",
                          id %in% "mentor_12" ~ "13",
                          id %in% "mentor_2" ~ "14",
                          id %in% "mentor_24" ~ "15",
                          id %in% "mentor_21" ~ "16",
                          id %in% "mentor_43" ~ "17",
                          id %in% "mentor_45" ~ "18",
                          id %in% "mentor_14" ~ "19",
                          id %in% "mentor_30" ~ "20",
                          id %in% "mentor_19" ~ "21",
                          id %in% "mentor_3" ~ "22",
                          id %in% "mentor_32" ~ "23",
                          id %in% "mentor_26" ~ "24",
                          id %in% "mentor_37" ~ "25",
                          id %in% "mentor_36" ~ "26",
                          id %in% "mentor_48" ~ "27",
                          id %in% "mentor_4" ~ "28",
                          id %in% "mentor_7" ~ "29",
                          id %in% "mentor_49" ~ "30",
                          id %in% "mentor_33" ~ "31",
                          id %in% "mentor_22" ~ "32",
                          id %in% "mentor_40" ~ "33",
                          id %in% "mentor_17" ~ "34",
                          id %in% "mentor_6" ~ "35",
                          id %in% "mentor_34" ~ "36",
                          id %in% "mentor_5" ~ "37",
                          TRUE ~ as.character("not paired"))) %>% 
           mutate(pair = as.factor(pair)) 
        
         
# now show me those who have NOT been paired

df_tor_to_pair <- df_tor %>% 
  filter(pair == "not paired") %>% 
  select(c(name, college, email))

# show the mentors who are paired & check the number of obs to my list

df_tor_check <- df_tor %>% 
  filter(pair != "not paired")

#check for duplicated pair numbers

df_tor_check %>% get_dupes(pair)



#### WRITE DATA ####
  
# when done pairing, write the data to a new file to make it easier to email folks & so I have a record
# row.names gets rid of the first column from the dataframe.

write.csv(df_tor_to_pair, here::here("00_data", "paired_data", "mentors_not_paired_prioritise_next_year.csv"), row.names = FALSE)


rm(df_tor_check)

```


```{r add pairing information for mentees}

# this is based on the pairing process that I completed. I am running this
  # up here so I can rerun some of the tables to show me only the folks who 
  # still need to be paired. I will not run this later for the final report.
  # The second number is the pair number.

df_tee <- df_tee %>% 
  mutate(pair = case_when(id %in% "mentee_47" ~ "01",
                          id %in% "mentee_41" ~ "02",
                          id %in% "mentee_40" ~ "03",
                          id %in% "mentee_51" ~ "04",
                          id %in% "mentee_10" ~ "05",
                          id %in% "mentee_13" ~ "06",
                          id %in% "mentee_2" ~ "07",
                          id %in% "mentee_7" ~ "08",
                          id %in% "mentee_29" ~ "09",
                          id %in% "mentee_49" ~ "10",
                          id %in% "mentee_35" ~ "11",
                          id %in% "mentee_16" ~ "12",
                          id %in% "mentee_32" ~ "13",
                          id %in% "mentee_52" ~ "14",
                          id %in% "mentee_17" ~ "15",
                          id %in% "mentee_50" ~ "16",
                          id %in% "mentee_3" ~ "17",
                          id %in% "mentee_45" ~ "18",
                          id %in% "mentee_24" ~ "19",
                          id %in% "mentee_12" ~ "20",
                          id %in% "mentee_25" ~ "21",
                          id %in% "mentee_6" ~ "22",
                          id %in% "mentee_43" ~ "23",
                          id %in% "mentee_8" ~ "24",
                          id %in% "mentee_48" ~ "25",
                          id %in% "mentee_36" ~ "26",
                          id %in% "mentee_15" ~ "27",
                          id %in% "mentee_39" ~ "28",
                          id %in% "mentee_26" ~ "29",
                          id %in% "mentee_34" ~ "30",
                          id %in% "mentee_14" ~ "31",
                          id %in% "mentee_28" ~ "32",
                          id %in% "mentee_37" ~ "33",
                          id %in% "mentee_53" ~ "34",
                          id %in% "mentee_46" ~ "35",
                          id %in% "mentee_31" ~ "36",
                          id %in% "mentee_1" ~ "37",
                          TRUE ~ as.character("not paired"))) %>% 
           mutate(pair = as.factor(pair)) %>% 
  relocate(pair, .after=id)
        
# now show me those who have not been paired

df_tee_to_pair <- df_tee %>%  
  filter(pair == "not paired") %>% 
  select(c(name, college, email))

# show the mentees who are paired

df_tee_check <- df_tee %>% 
  filter(pair != "not paired")

#check for duplicated pair numbers

df_tee_check %>% get_dupes(pair)


#### WRITE DATA ####
  
# when done pairing, write the data to a new file to make it easier to email folks
# row.names gets rid of the first column from the dataframe.
# none this year

# write.csv(df_tee_to_pair, here::here("paired_data", "not_paired_prioritise_next_year.csv"), row.names = FALSE)

rm(df_tee_check, df_tee_to_pair)

```


```{r join the tibbles, include = FALSE}

# join everyone who is paired

# add college abbreviations and change the type of variables to characters, so I can join them  

df_tee <- df_tee %>%
  filter(pair != "not paired") %>%
  mutate(
    college_abb = case_when(college %in% "Business, Government and Law" ~ "CBGL",
      college %in% "Education, Psychology and Social Work" ~ "CEPSW",
      college %in%  "Humanities, Arts and Social Sciences" ~ "CHASS",
      college %in%  "Nursing and Health Sciences" ~ "CNHS",
      college %in%  "Medicine and Public Health" ~ "CMPH",
      college %in%  "Science and Engineering" ~ "CSE",
      TRUE ~ as.character("")
    )
  ) %>% 
  unite ("name and college_abb", c(name,college_abb), sep = " - ", remove = FALSE) %>% 
  mutate_if(is.numeric, as.character)

# final number of mentees selected for the program
total_tee <- nrow(df_tee)

df_tor <- df_tor %>% 
  filter(pair != "not paired") %>% 
    mutate(
    college_abb = case_when(college %in% "Business, Government and Law" ~ "CBGL",
      college %in% "Education, Psychology and Social Work" ~ "CEPSW",
      college %in%  "Humanities, Arts and Social Sciences" ~ "CHASS",
      college %in%  "Nursing and Health Sciences" ~ "CNHS",
      college %in%  "Medicine and Public Health" ~ "CMPH",
      college %in%  "Science and Engineering" ~ "CSE",
      TRUE ~ as.character("")
    )
  ) %>% 
  unite ("name and college_abb", c(name,college_abb), sep = " - ", remove = FALSE) %>% 
  mutate_if(is.numeric, as.character)

# final number of mentees selected for the program
total_tor <- nrow(df_tor)

#combine the paired mentor and mentee tibbles into one

df <- full_join(df_tor, df_tee)

# then use this for additional processing

```


Table \ref{tab:college_breakdown} shows the number of mentees and mentors per 
College who were selected to participate in the program. 

For the first time ever, we have had more mentors express an interest in the 
program than mentees. This is likely the result of our concerted efforts to 
attract more mentors to the program along with the possibility that we are 
adequately meeting the demand from our Early Career Researcher community, 
given the larger cohorts that we have had in the previous 3 years (30--38 pairs, 
compared to 12--20 pairs in the past). 

We are reserving the `r nrow(df_tor_to_pair)` mentors that we were unable to 
match as backup in case any of our other mentors are unable to participate in the 
program. We will also prioritise their involvement in the program next year so they
have a chance to develop and implement their mentoring skills and expand their 
network at Flinders. 

We also had one mentor and one mentee withdraw for personal reasons soon after the program
began. We were able to pair the remaining mentee and mentor from each pair with
each other. As such, we had 37 pairs in the program since March 2025. 

The percentage column represents the percentage of mentors from each 
College and the percentage of mentees from each College who are participating
in this year's program. As evident from this table, 
the College of Humanities, Arts and Social Sciences had a larger percentage of mentors
compared to the percentage of mentees in the program this year. 
The College of Medicine and Public Health had the largest 
percentage of mentees in the program, which was not the case for the mentors. The 
other Colleges had similar percentages of mentees and mentors in the program. 


```{r college_breakdown, include=TRUE}

# how many mentors per college

col_tor <- df_tor %>% 
  group_by(college) %>% 
  summarise(n = n()) %>% 
  mutate(perc = round(100*(n / sum(n)),2)) %>% 
  arrange(college) %>% 
  ungroup

col_tee <- df_tee %>% 
  group_by(college) %>% 
  summarise(n = n()) %>% 
  mutate(perc = round(100*(n / sum(n)),2)) %>% 
  arrange(college) %>% 
  ungroup


col <- full_join (col_tor, col_tee, by = "college") %>% 
    replace(is.na(.), 0)

# need to manually update the number of mentors and mentees in the header

col %>% 
knitr::kable (booktabs = T, linesep = "",
              col.names = c("College", "Number", "Percentage", "Number", "Percentage"), 
              caption = "Breakdown of Mentors and Mentees by College",
              align = 'lcc') %>% 
    add_header_above(c(" " = 1, "Mentors (n = 37)" = 2, "Mentees (n = 37)" = 2)) %>% 
  styler_pdf() 


```

\newpage

Table \ref{tab:mentor_details} shows the details of the mentors who were selected 
to participate in the program. 


```{r mentor_details, include=TRUE}

# identify the mentors in each college

col_tor_details <- df_tor %>% 
  select (c(college, name, level_recode)) %>% 
  arrange(college) %>% 
  ungroup


knitr::kable (
  col_tor_details[, c(2,3)],
  booktabs = T,
  linesep = "",
  col.names = c("Names", "Levels"),
  caption =
    sprintf("Breakdown of Mentors by College (n = %d)",
            total_tor),
  align = 'lcc'
  ) %>%
  pack_rows (index = table(col_tor_details$college)) %>%
  styler_pdf()


```

\newpage

Table \ref{tab:mentee_details} shows the details of the mentees who were selected 
to participate in the program. 

```{r mentee_details, include=TRUE}

# identify the mentees in each college

col_tee_details <- df_tee %>% 
  select (c(college, name, level_recode)) %>% 
  arrange(college) %>% 
  ungroup


knitr::kable (
  col_tee_details[, c(2,3)], # select only the names and levels columns
  booktabs = T,
  linesep = "",
  col.names = c("Names", "Levels"),
  caption =
    sprintf("Breakdown of Mentees by College (n = %d)",
            total_tee),
  align = 'lc', 
  longtable = T #break the table over multiple pages
  ) %>%
  pack_rows (index = table(col_tee_details$college)) %>%
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position", "striped")) 
# use different styling to repeat the header

```




```{r mentee_details_expansive, include=FALSE}

# we used this detail for the mentee roundtable for HDR supervision. This isn't
  # part of the regular report. 

# This is the text for the intro to the table.

# \newpage
# 
# Table \ref{tab:mentor_details} shows the details of the mentors who were selected 
# to participate in the program. 


# identify the mentees in each college

col_tee_details_more <- df_tee %>% 
  select (c(college, name, level_recode, position, employment_length)) %>% 
  arrange(college) %>% 
  ungroup


knitr::kable (
  col_tee_details_more[, c(2:5)], # select only the names and levels columns
  booktabs = T,
  linesep = "",
  col.names = c("Names", "Levels", "Position", "Employment"),
  caption =
    sprintf("Breakdown of Mentees by College (n = %d)",
            total_tee),
  align = 'lcll', 
  longtable = T #break the table over multiple pages
  ) %>%
  pack_rows (index = table(col_tee_details_more$college)) %>%
    column_spec(3, width = "3in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position", "striped")) 
# use different styling to repeat the header

```

\newpage

Table \ref{tab:pairs_details_for_report} shows which mentor each mentee was paired with. 

```{r pairs_details_for_pairing_test, include=TRUE, eval = FALSE}

# select the key info that I want to show

pairs <- df %>% 
  select(pair, first_name, name, college, `name and college`, `name and college_abb`, email, role) %>% 
  arrange(pair) %>% 
  ungroup

# number of pairs

n_pairs <- length(unique(pairs$pair))

pairs_by_role <- pairs %>% 
  pivot_wider(
    names_from = role,
    values_from = c(first_name, name, college, `name and college`, `name and college_abb`, email)
  ) %>% 
  relocate(contains("_mentor"), .after = last_col())

# # decide which version I want
# simple_pairs <- pairs_by_role %>% 
#   select(-c(contains(c("email", "first_name", "name and college"))))

# # decide which version I want [if I select this version, I will have to change the kable]
# simple_pairs <- pairs_by_role %>% 
# select(-c(college_mentor, college_mentee, name_mentee, name_mentor, contains(c("email", "first_name"))))

# USE THIS VERSION BECAUSE IT KEEPS EVERYTHING ON ONE LINE

simple_pairs <- pairs_by_role %>%
select(-c(college_mentor, college_mentee, name_mentee, name_mentor, `name and college_mentee`,
          `name and college_mentor`, contains(c("email", "first_name")))) %>% 
      arrange ()


simple_pairs %>% 
  knitr::kable (booktabs = F, linesep = "\\addlinespace",
  col.names = c("Pair", "Mentee", "Mentor"),
  caption = sprintf("Details of Matched Pairs (n = %d)",
            n_pairs),
  align = 'cll', 
  longtable = T) %>%
  column_spec(2, width = "3in") %>% 
  column_spec(3, width = "3in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position", "striped"))



#### WRITE DATA ####
  
# when done preprocessing, write the data to new files
# row.names gets rid of the first column from the dataframe.

write.csv(simple_pairs, here::here("00_data", "paired_data", "pairs.csv"), row.names = FALSE)


```

\renewcommand{\arraystretch}{1.5}
```{r pairs_details_for_report, include=TRUE}

# latex code above adds whitespace to the table: https://stackoverflow.com/questions/53794142/increase-line-row-spacing-with-kableextra

# select the key info that I want to show [remove pair number for the final report]

pairs <- df %>% 
  select(pair, first_name, name, college, `name and college`, `name and college_abb`, email, role) %>% 
  arrange(pair) %>% 
  ungroup

# number of pairs

n_pairs <- length(unique(pairs$pair))

pairs_by_role <- pairs %>% 
  pivot_wider(
    names_from = role,
    values_from = c(first_name, name, college, `name and college`, `name and college_abb`, email)
  ) %>% 
  relocate(contains("_mentor"), .after = last_col())

# # decide which version I want
# simple_pairs <- pairs_by_role %>% 
#   select(-c(contains(c("email", "first_name", "name and college"))))

# # decide which version I want [if I select this version, I will have to change the kable]
# simple_pairs <- pairs_by_role %>% 
# select(-c(college_mentor, college_mentee, name_mentee, name_mentor, contains(c("email", "first_name"))))

# USE THIS VERSION BECAUSE IT KEEPS EVERYTHING ON ONE LINE

simple_pairs <- pairs_by_role %>%
select(-c(pair, college_mentor, college_mentee, name_mentee, name_mentor, `name and college_mentee`,
          `name and college_mentor`, contains(c("email", "first_name")))) %>% 
      arrange (`name and college_abb_mentee`, `name and college_abb_mentor`)


simple_pairs %>% 
  knitr::kable (format = "latex",
                booktabs = TRUE, 
                linesep = "", #removes the extra space every 5 rows
  col.names = c("Mentee", "Mentor"),
  caption = sprintf("Details of Matched Pairs (n = %d)",
            n_pairs),
  align = 'll', 
  longtable = T) %>%
  column_spec(1, width = "3in") %>% 
  column_spec(2, width = "3in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position", "striped"))



#### WRITE DATA ####
  
# when done preprocessing, write the data to new files
# row.names gets rid of the first column from the dataframe.

write.csv(simple_pairs, here::here("00_data", "paired_data", "pairs.csv"), row.names = FALSE)


```



```{r pairs details for emails, eval = TRUE}

# get the email details 
  
pairs_by_role_emails <- pairs_by_role %>% 
  select(-contains(c("first_name", "name and college")))
  
  
#### WRITE DATA ####
  
# when done pairing, write the data to a new file to make it easier to email folks
# row.names gets rid of the first column from the dataframe.

write.csv(pairs_by_role_emails, here::here("00_data", "paired_data", "pairs_with_emails.csv"), row.names = FALSE)


```

```{r details for mail merge, eval = TRUE, include = FALSE}

# edit the text so I can copy the name and college from excel

pairs_by_role <- pairs_by_role %>% 
  mutate (`name_and_college_mentor` = str_replace(`name and college_mentor`, " - ", " from the College of ")) %>% 
    mutate (`name_and_college_mentee` = str_replace(`name and college_mentee`, " - ", " from the College of "))

for_mentees_for_merge <- pairs_by_role %>% 
  select(c(email_mentee, first_name_mentee, name_and_college_mentor, first_name_mentor)) %>% 
  relocate(email_mentee, .after = last_col())

for_mentors_for_merge <- pairs_by_role %>% 
  select(c(email_mentor, first_name_mentee, name_and_college_mentee, first_name_mentor)) %>% 
    relocate(email_mentor, .after = last_col())

#### WRITE DATA ####
  
# write a new file for both roles for use with mail merge

write.csv(for_mentors_for_merge, here::here("00_data", "paired_data", "for_mentors_with_merge.csv"), row.names = FALSE)

write.csv(for_mentees_for_merge, here::here("00_data", "paired_data", "for_mentees_with_merge.csv"), row.names = FALSE)

```


```{r dietary details, eval = FALSE}

dietary <- df %>% 
  select(role, name, dietary) %>% 
  arrange(name) %>% 
  ungroup

dietary %>% 
  knitr::kable (booktabs = T, linesep = "\\addlinespace",
  col.names = c("Role", "Name", "Dietary"),
  caption = "Dietary Requirements", 
  align = 'lll', 
  longtable = T) %>%
  column_spec(2, width = "3in") %>% 
  column_spec(3, width = "3in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position", "striped"))

#### WRITE DATA ####
  
# when done preprocessing, write the data to new files
# row.names gets rid of the first column from the dataframe.

write.csv(dietary, here::here("00_data", "paired_data", "dietary.csv"), row.names = FALSE)

```


```{r campus details, eval = FALSE}

campus <- df %>% 
  select(role, name, email, campus) %>% 
  arrange(name) %>% 
  ungroup

campus %>% 
  knitr::kable (booktabs = T, linesep = "\\addlinespace",
  col.names = c("Role", "Name", "Email", "Campus"),
  caption = "Where are participants are located", 
  align = 'llll', 
  longtable = T) %>%
  column_spec(2, width = "3in") %>% 
  column_spec(3, width = "3in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position", "striped"))

#### WRITE DATA ####
  
# when done preprocessing, write the data to new files
# row.names gets rid of the first column from the dataframe.

write.csv(campus, here::here("00_data", "paired_data", "campus.csv"), row.names = FALSE)

```

```{r output names for colleges, eval = FALSE}

# use this to send the list of names to the colleges

# BGL

bgl_tee <- df_tee %>% filter(str_detect(college, "Business")) %>% select(name)
bgl_tor <- df_tor %>% filter(str_detect(college, "Business")) %>% select(name)

# EPSW

epsw_tee <- df_tee %>% filter(str_detect(college, "Education")) %>% select(name)
epsw_tor <- df_tor %>% filter(str_detect(college, "Education")) %>% select(name)

# HASS

hass_tee <- df_tee %>% filter(str_detect(college, "Humanities")) %>% select(name)
hass_tor <- df_tor %>% filter(str_detect(college, "Humanities")) %>% select(name)

# mph

mph_tee <- df_tee %>% filter(str_detect(college, "Medicine")) %>% select(name)
mph_tor <- df_tor %>% filter(str_detect(college, "Medicine")) %>% select(name)

# NHS

nhs_tee <- df_tee %>% filter(str_detect(college, "Nursing")) %>% select(name)
nhs_tor <- df_tor %>% filter(str_detect(college, "Nursing")) %>% select(name)

# SE

se_tee <- df_tee %>% filter(str_detect(college, "Engineering")) %>% select(name)
se_tor <- df_tor %>% filter(str_detect(college, "Engineering")) %>% select(name)

## I must be able to build a function for this, but not today! this is my 
  # inspiration

# tee_by_college <- function(college, folder = here::here("paired_data")) {
#   
#     tee_filtered <- df_tee %>% 
#     filter(college %in% c("Medicine and Public Health", college) %>% 
#              mutate(college = fct_inorder(college)) 
# 
# }
# 
# 
# 
# write.csv(tee_filtered, file = str_glue("tee_{college}.csv"), row.names = FALSE)

write <- function(x, file, folder = here::here("00_data", "paired_data")) {
  write.csv(x, file = str_glue("tee_(x).csv"))
}

write(x = bgl_tee)

```

```{r network analysis, eval = FALSE}

# I need to keep working on this. I got lost at the v.size

# from this tutorial: https://ladal.edu.au/net.html 

nodes <- pairs_by_role %>% 
  count(college_mentee) %>% 
  rename(`Mentee College` = college_mentee)

net <- count (pairs_by_role, college_mentee, college_mentor, name = "Freq")

nodes_df <- data.frame(nodes)
net_df <- data.frame(net)

ig <- igraph::graph_from_data_frame(d = net_df, vertices = nodes_df, directed = FALSE)

tg <- tidygraph::as_tbl_graph(ig) %>% 
  tidygraph::activate(nodes) %>% 
  dplyr::mutate(label = name)

set.seed(12345)

# determine the size of the node
v.size <- net_df$Freq
v.size

# plot it all
tg %>% 
  ggraph (layout = "fr") +
  geom_edge_arc(colour = "gray50", 
                 lineend = "round", 
                 strength = .1,
                 alpha = .1) +
#  geom_node_point(size = log(v.size)*2) +
  geom_node_text(aes(label = name), 
                 repel = TRUE,
                 point.padding = unit (0.2, "lines"), 
                 colour = "gray10") +
  theme_graph(background = "white") + 
  guides (edge_width = FALSE, 
          edge_alpha = FALSE)



```



If you have any questions, please contact Dr Jen Beaudry, Manager, Researcher Training, Development and Communication in Research Development and Support. 
